\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2022-02-06 manuscript.Rmd
Manuscript Restuctured: Now has a better flow. Flowchart updated

Data was collected in a quantitative cross-sectional approach via a fully anonymous online survey hosted on REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch). Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) of a Comic co-released with the survey[@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux [@f.lux].
Completing the online survey took approx. 15 to 20 minutes and was not compensated. The first page of the survey comprised a participant information sheet, where participants' informed consent to participate was obtained before any of the questions were displayed. Underaged participants (<18 years) were urged to obtain assent from their parents/legal guardians, before filling in the survey. Information on the first page included the objectives of the study, inclusion criteria, estimated duration, the use, storage and sharing of the data, compensation (none), and information about the type of questions in the survey. Moreover, participants needed to confirm that they were participating the survey for the first time. To ensure high data quality, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention. What is 4+5?"). The data analysed in this study was collected between 17 May 2021 and 3 September 2021. Questions incorporating retrospective recall were all aligned to the period of "past four weeks", matching the presented LEBA instrument.

In addition to the LEBA questionnaire, which is subject of the current study, we assessed other variables and items which were not included in the present analysis. This comprised various sleep-related measures, i.e., sleep disturbances and sleep-related impairment (adult and pediatric versions) [@Bevans.2019; @Buysse.2010; @Forrest.2018; @Harb.2015; @Yu.2011], sleep duration, timing, and latency, chronotype, social jetlag, time in bed, work/sleep schedule and outdoor light exposure duration [MCTQ version for adults and adolescents @roenneberg2003life] plus sleep environment [@Olivier.2016]. Furthermore, we included a light sensitivity questionnaire (photophobia vs. photophilia) [@Wu.2017] and self-reported pubertal stage assessment [@Petersen.1988] for participants younger than 18 years of age. Moreover, we incorporated custom items on meal timing and caffeine consumption in the “workday vs. free day” structure of the MCTQ sleep-wake regulation. Example items are: “On workdays I usually have my first meal at __:__”, “On free days I usually have my last meal at __:__”, and “On workdays I usually drink my first caffeinated drink at __:__”.

Finally, we assessed age, sex, gender identity, occupational status, COVID-19 related occupational setting, time zone/country of residence and native language as single-item demographic variables. The demographic characteristics of our sample are given in Table \@ref(tab:demotab).

@@

                    A[label = '48 items were generated'] 
                    B[label = 'Exploratory Factor Analysis on 48 Items (n = 428)']

                    node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 16, height = 6, 
                    fixedsize = true, fontsize = 45]
                    C[label = 
                    <Factor Identification<br/>Scree Plot: 6 Factors<br/>Parallel Analysis: 6 Factors<br/>Minimum Average Partial Method: 5 Factors<br/>Hull Method: 5 Factors>
                    ]

@@

                    4[label = <Confirmatory Factor Analysis<br/>on the Five Factor Model (23 Items; n=262)<br/>Acceptable Fit ( CFI = .97; TLI= .96; RMSEA = .04, SRMR = .09)>]
                     5[label = <Reliability Analysis (23 Items; n=262)<br/>Ordinal alpha F1=.93; F2=.83; F3 =.70; F4=.69; F5=.52<br/>Mcdonald  omega(total) for the total scale = .73>]
                    8[label = <Measurement Invariance Analysis<br/>Residual measurement invariance achieved>]
                    9[label = 'Semantic Analysis']
                    10[label = <LEBA Short Form (18 Items; n=690)<br/>Based on Item Response Theory>]
                    }
                subgraph cluster_2 {
                      graph[fontname = Helvetica,shape = rectangle]
                      style = rounded
                     node[fontname = Helvetica, margin = 0.2,width = 18, height = 2.5, 
                fixedsize = true, fontsize = 45 ]
                    6[label = 
                    <6-Factor solution:<br/>one factor emerged with only two salient loadings>
                    ]
                    7[label = 'Rejected']
                    }

                     edge[fontname = Helvetica,color = black,arrowhead = vee, arrowsize = 1.25]
                     A ->B
                     B ->C
                     C ->1
                     1 ->2
                     2 ->3
                     3 ->4
                     4 ->5
                    5->8
                    8 ->9
                    9 ->10
                     C ->6
                     6 ->7

@@

## Item Construction & Item Selection

@@

Figure \@ref(fig:FlowchartFig) summarizes the steps of our psychometric analysis. In our analysis we used R (version 4.1.0), with several R packages. Initially, our tool had six point Likert type response format (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5:Always). Our purpose was to capture light exposure related behavior and these two response options: "Does not apply/I don't know" and "Never" were providing similar information. As such we decided to collapse them into one, making it a 5 point Likert type response format. We conducted an initial item analysis and proceed to the EFA. Prior to the EFA,necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed. Our data violated both the univariate and multivariate normality assumptions. Due to these violations and the ordinal nature of our response data, we used  polychoric correlation matrix [@desjardinsHandbookEducationalMeasurement2018] for the EFA. We employed principal axis (PA) as  factor extraction method with varimax rotation. PA is robust to the normality assumption violations [@watkinsStepbyStepGuideExploratory2020]. The obtained latent structure was confirmed by another factor extraction method: "the minimum residuals extraction" as well. We used a combination of factor identification method including scree plot [@cattellScreeTestNumber1966], minimum average partials method [@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers. Additionally, to determine the simple structure, we followed the common guidelines : (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading > .3 across factors [@bandalosFactorAnalysisExploratory2018]. We also conducted a EFA on non-merged response options data (Supp. Table \@ref(tab:efaunmerged)) and rejected the latent structure obtained as the factors were less interpretable.

For estimating reliability we used internal consistency reliability coefficient ordianl alpha. Though  Cronbach's alpha coefficient is widely used for estimating internal consistency, it has a tendency to deflate the estimates for  Likert type data since calculation is based on pearson-correlation matrix which requires response data to be continuous of nature [@gadermann2012estimating; @zumbo2007ordinal]. Subsequently to get  better estimates of reliability  we reported ordinal alpha that used polychoric-correlation matrix and assumed that the responses data were ordered in nature instead of continuous [@zumbo2007ordinal]. Ordinal alpha coefficient value ranges from 0 to 1 and higher value represents better reliability.

@@

```{r, MIdescription, include =F}
# Among these nested models  configural model is the first and least restrictive model. The configural model assumes that the number of factors and item number under each factor will be equal across two groups. The metric invariance model assumes configural invariance of the fitted model and requires the factor-loadings of the items across the two groups to be equal. Having the factor-loadings equal across groups indicates each item contributes to the measured construct equivalently. Scalar invariance assumes the metric invariance of the fitted model demands the item intercepts to be equivalent across groups. This equity of item intercepts indicates the equivalence of response scale across the groups, i.e., persons with the same level of the underlying construct will score the same across the groups. The residual invariance model assumes metric invariance for the fitted model and adds the assumption of equality in error variances and covariances across the groups. This model is the highest level of MI and assures the equivalence of precision of items across the groups in measuring the underlying constructs.  We assessed the invariance model fit  using the fit by following the aforementioned guidelines of modelfit. The comparison among the MI models was made using 
```

@@

## Participants

```{r demotab, warning=F, message=F}
desc_kable  %>% kable_styling(latex_options = c("scale_down")) %>% landscape()
```

Table \@ref(tab:demotab) summarizes the survey participants' demographic characteristics. Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses. XX participants were excluded from analysis due to not passing at least one of the "attention check" items. For exploring initial factor structure (EFA), a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013]. For estimating the sample size for the confirmatory factor analysis (CFA) we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where ten participants per parameter is required to earn trustworthiness of the result. Our sample size exceeds these requirements: Anonymous responses from a total of *n* = `r nrow(desctable.data)` participants were included in the analysis of the current study, split into samples for exploratory (EFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "1. EFA Sample",])`) and confirmatory factor analysis (CFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "2. CFA Sample",])`). The EFA sample included participants filling out the questionnaire from 17 May 2021 to XX XXX 2021, whereas participants who filled out the questionnaire from YY YYY 2021 to 3 September 2021 were included in the CFA analysis. Participants indicated filling out the online survey from a diverse range of geographic locations. The ten most common country and time zone combinations included:

@@

## Item Analysis

@@

## Exploratory Factor Analysis
```{r CorrMatrix, include=FALSE}
#This chunk holds code for producing correlation matrix and its details.

@@

Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy [@kaiserIndexFactorialSimplicity1974] . The overall KMO vale for 48 items was `r printnum(KMO$MSA)` which was above the cutoff value (.50) indicating a mediocre sample [@hutchesonMultivariateSocialScientist1999].  Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p < .001 indicated the correlations between items are adequate for the EFA. However only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than .30. The absolute value of inter-item correlation ranged between `r min.cor` to `r max.cor`. Figure \@ref(fig:figCor) depicts the correlation matrix.
```{r tabDes,results='asis'}
descriptives2 %>% 
apa_table(landscape =T,caption ="Descriptive Statistics", escape =F, font_size = "footnotesize", note = "*p<.001", align = c("p{1cm}","p{10cm}", rep("p{1cm}", ncol(descriptives2)))) 
```

@@

Scree plot ( Figure \@ref(fig:facIdFig)) suggested a six-factor solution. However, the minimum average partial (MAP) [@velicerDeterminingNumberComponents1976] method (Table \@ref(tab:factormp)) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:facIdFig)) suggested a five-factor solution. As a result, we tested both five-factor and six-factor solutions.
```{r factors, include=F}
#This chunk holds code for compiled factor identification plots

@@

```
## Confirmatory Factor Analysis

@@

Table \@ref(tab:tabCfa) summarizes the CFA fit indices of our fitted model. Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`); RMSEA = `r apa(fit.1[7],2,F)`,[`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 [`r Hmisc::label(sem.data$item32)`;`r Hmisc::label(sem.data$item33)`] and 16-17 [`r Hmisc::label(sem.data$item16)`;`r Hmisc::label(sem.data$item17)`]. Items pair 32-33 stemed from the preference of dimming electric device's brightness before bed time and items pair 16 and 19 stemed from the preference of using blue filtering or colored glasses during the daytime. Nevertheless, SRMR value was higher than the guideline (SRMR = `r apa(fit.1[10],2,F)`). Further by allowing one pair of items (30-41) [`r Hmisc::label(sem.data$item30)`;`r Hmisc::label(sem.data$item41)`] to covary their error variance and discarding two item (item 37 & 26) for very low r-square value, our model attained best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]) and SRMR value (SRMR = `r apa(fit.2[10],2,F)`) was also close to the suggestions of @huCutoffCriteriaFit1999. Internal consistency ordinal $\alpha$ for the five factors of LEBA were `r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)` respectively. We also estimated the internal consistency reliability of the total scale using Mcdonald's $\omega_t$  coefficient which is a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use]. McDonald's $\omega_t$ coefficient for the total scale was `r apa(rel.k[5,6],2,F)`. Figure \@ref(fig:figcfa) depicts the obtained CFA structure.

@@

## Measurement Invariance
```{r InvarianceAnalysis_data, include=FALSE}
#This chunk holds codes to prepare measurement invariance data.

@@

In our CFA sample we had `r mi.count[1,2]`  **native English speakers** and `r mi.count[2,2]` **non-native English speakers**  (For a detailed description these two groups see Sup. Table \@ref(tab:midesp)). Table \@ref(tab:InvarianceTab) indicates our fitted model had acceptable fit indices for all of the fitted MI models. The model fit did not significantly decrease across the nested models indicating the acceptability of the higheest measurement invariance model : residualmodel.

@@

## Semantic Analysis 
To find out if our developed tool (23 items) is overlapping with existing instruments, we subjected the items of LEBA to the "Semantic Scale Network"(SSN) analysis [@rosenbusch2020semantic]. The SSN detects semantically related scales and provides cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic]. Pair of scales with a cosine similarity index value of 1 indicates they are perfectly semantically similar scales indicating redundancy. LEBA  appeared most strongly related to scales about sleep: "Sleep Disturbance Scale For Children" [@bruni1996sleep] and "WHO-Composite International Diagnostic Interview (CIDI): Insomnia"[@who1990].The cosine similarities lie between .47 to .51. Flesch-Kincaid Grade Level [@flesch1948new] analysis on the the 23 items of our scale indicated required educational grade level was 3.33 and with a age above 8.33.
```{r textanalysis}
#This chunk holds codes for semantic analysis and readability test

@@

## Developing Short form of LEBA
We sought the Item Response Theory (IRT) to develop the short form of LEBA. IRT the conventional classical test theory-based analysis by gathering information on item quality by indices like item difficulty, item discrimination, and item information [@bakerBasicsItemResponse2017]. Item is  judged based on item information in relation to participants' latent trait level ($\theta$). We fitted each factor of LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =690). Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait level ($\theta$), and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum. Here, we reported the item discrimination parameter and only discarded the items with relatively flat item information curve (information <.2) to develop the short form of LEBA. @bakerBasicsItemResponse2017 categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high >1.70. Table \@ref(tab:IRTparameters) summarizes the IRT parameters of our tool. Item discrimination parameters of our tool fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level ($\theta$). Examination of the item information curve (Sup.fig \@ref(fig:IF)) indicated 5 items (1, 25,  38, 30, & 41) had relatively flat information curves (I($\theta$) <.20) thus discarded creating a short form of LEBA with 5 factors and 18 items.

@@

```{r factorinfo, eval=FALSE, include=FALSE}
#This chunk holds codes for item info plots clustered in factors (Not included in the manuscript)
F1.itemplots <- cowplot::plot_grid(F1.iteminfo.1,F1.iteminfo.2, F1.iteminfo.3,
                   labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "Arial",
  label_fontface = "plain")
ggsave("Manuscript.figures/F1.itemplots.png",F1.itemplots, width = 10, height = 12, dpi = 600,bg = "white")

F2.itemplots <- cowplot::plot_grid(F2.iteminfo.1,F2.iteminfo.2, F2.iteminfo.3,
                                   F2.iteminfo.4,F2.iteminfo.5,F2.iteminfo.6,
                   labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "Arial",
                     label_fontface = "plain")
ggsave("Manuscript.figures/F2.itemplots.png",F2.itemplots, width = 10, height = 12, dpi = 600, bg = "white")

F3.itemplots <- cowplot::plot_grid(F3.iteminfo.1,F3.iteminfo.2, F3.iteminfo.3,
                                   F3.iteminfo.4,F3.iteminfo.5,
                 labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "Arial",
                     label_fontface = "plain")
ggsave("Manuscript.figures/F3.itemplots.png",F3.itemplots, width = 10, height = 12, dpi = 600,bg = "white")

F4.itemplots <- cowplot::plot_grid(F4.iteminfo.1,F4.iteminfo.2, F4.iteminfo.3,
                                   F4.iteminfo.4,
                   labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "Arial",
                     label_fontface = "plain")
ggsave("Manuscript.figures/F4.itemplots.png",F4.itemplots, width = 10, height = 12, dpi = 600,bg = "white")

F5.itemplots <- cowplot::plot_grid(F1.iteminfo.1,F1.iteminfo.2, F1.iteminfo.3,

                   labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "Arial",
                     label_fontface = "plain")
ggsave("Manuscript.figures/F5.itemplots.png",F5.itemplots, width = 10, height = 12, dpi = 600, bg = "white")

```{r inteminfoggplo2c, eval=FALSE, include=FALSE}
# This chinks holds code of compiled item info code created using facet wrap. (Not included in manuscript)
pacman::p_load(reshape,ggsci)
Theta <- matrix(seq(-6,6, by = .1))

##Item Info
Item16 <- iteminfo(F1.item1, Theta)
Item36 <- iteminfo(F1.item2, Theta)
Item17 <- iteminfo(F1.item3, Theta)
Item11 <- iteminfo(F2.item1, Theta)
Item10 <- iteminfo(F2.item2, Theta)
Item12 <- iteminfo(F2.item3, Theta)
Item07 <- iteminfo(F2.item4, Theta)
Item08 <- iteminfo(F2.item5, Theta)
Item09 <- iteminfo(F2.item6, Theta)
Item27 <- iteminfo(F3.item1, Theta)
Item03 <- iteminfo(F3.item2, Theta)
Item40 <- iteminfo(F3.item3, Theta)
Item30 <- iteminfo(F3.item4, Theta)
Item41 <- iteminfo(F3.item5, Theta)
Item32 <- iteminfo(F4.item1, Theta)
Item35 <- iteminfo(F4.item2, Theta)
Item38 <- iteminfo(F4.item3, Theta)
Item33 <- iteminfo(F4.item4, Theta)
Item46 <- iteminfo(F5.item1, Theta)
Item45 <- iteminfo(F5.item2, Theta)
Item25 <- iteminfo(F5.item3, Theta)
Item04 <- iteminfo(F5.item4, Theta)
Item01 <- iteminfo(F5.item5, Theta)

F1.item.info.data <- as.data.frame(cbind(Item16, 
                                              Item36,
                                              Item17))

F2.item.info.data <- as.data.frame(cbind(Item11, 
                                              Item10,
                                              Item12,
                                         Item07,
                                         Item08,
                                         Item09))

F3.item.info.data <- as.data.frame(cbind(Item27, 
                                              Item03,
                                              Item40,
                                         Item30,
                                        Item41))

F4.item.info.data <- as.data.frame(cbind(Item32, 
                                              Item35,
                                              Item38,
                                         Item33))
F5.item.info.data <- as.data.frame(cbind(Item46, 
                                              Item45,
                                             Item25,
                                         Item04,
                                         Item01))

F1.item.info.data.long <- melt(F1.item.info.data)
F2.item.info.data.long <- melt(F2.item.info.data)
F3.item.info.data.long <- melt(F3.item.info.data)
F4.item.info.data.long <- melt(F4.item.info.data)
F5.item.info.data.long <- melt(F5.item.info.data)

>>>>

```{r rafel, include=F}
# In addition to the LEBA questionnaire, which is subject of the current study, we assessed other variables and items which were not included in the present analysis. This comprised various sleep-related measures, i.e., sleep disturbances and sleep-related impairment (adult and pediatric versions) [@Bevans.2019; @Buysse.2010; @Forrest.2018; @Harb.2015; @Yu.2011], sleep duration, timing, and latency, chronotype, social jetlag, time in bed, work/sleep schedule and outdoor light exposure duration [MCTQ version for adults and adolescents @roenneberg2003life] plus sleep environment [@Olivier.2016]. Furthermore, we included a light sensitivity questionnaire (photophobia vs. photophilia) [@Wu.2017] and self-reported pubertal stage assessment [@Petersen.1988] for participants younger than 18 years of age. Moreover, we incorporated custom items on meal timing and caffeine consumption in the “workday vs. free day” structure of the MCTQ sleep-wake regulation. Example items are: “On workdays I usually have my first meal at __:__”, “On free days I usually have my last meal at __:__”, and “On workdays I usually drink my first caffeinated drink at __:__”.

@@

                    A[label = 'Initial Development of 48 Items'] 
                    B[label = 'Large Scale Survey (n=690)']
                    C[label = 'Initial Item Analysis']
                    D[label = 'Exploratory Factor Analysis (48 items; n=428)']

                    node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 16, height = 6, 
                    fixedsize = true, fontsize = 45]
                    E[label = 
                    <Factor Identification<br/>Scree Plot: 6 Factors<br/>Minimum Average Partial Method: 5 Factors<br/>Hull Method: 5 Factors>
                    ]

@@

                    4[label = <Confirmatory Factor Analysis<br/>on the Five Factor Model (23 Items; n=262)<br/>Acceptable Fit ( CFI = .97; TLI= .96; RMSEA = .04, SRMR = .09)>]
                     5[label = <Reliability Analysis (23 Items; n=262)<br/>Ordinal alpha F1=.93; F2=.83; F3 =.70; F4=.69; F5=.52<br/>Mcdonald  omega(total) for the total scale = .73>]
                    8[label = <Measurement Invariance Analysis (n=262)<br/>Residual measurement invariance achieved>]
                    9[label = <Semantic Analysis (n=262):<br/>Semantic Scale Network analysis<br/>Readbility: Grade level 3.33>]
                    10[label = <LEBA Short Form (19 Items; n=690)<br/>Based on Item Response Theory>]
                    }
                subgraph cluster_2 {
                      graph[fontname = Helvetica,shape = rectangle]
                      style = rounded
                     node[fontname = Helvetica, margin = 0.2,width = 18, height = 2.5, 
                fixedsize = true, fontsize = 45 ]
                    6[label = 
                    <6-Factor solution:<br/>one factor emerged with only two salient loadings>
                    ]
                    7[label = 'Rejected']
                    }

                     edge[fontname = Helvetica,color = black,arrowhead = vee, arrowsize = 1.25]
                     A ->B
                     B ->C
                     C ->D
                     D ->E
                E ->1
                     1 ->2
                     2 ->3
                     3 ->4
                     4 ->5
                    5->8
                    8 ->9
                    9 ->10
                     E ->6
                     6 ->7

@@

A quantitative cross-sectional fully anonymous online survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch). Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) of a Comic co-released with the survey[@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux [@f.lux]. The landing page of the on-line survey had the explanatory statements It was mentioned in the explanatory statement that their participation was voluntary and that they could withdraw from participation anytime without being penalized. At the beginning of the survey, for the adult participants (>18 years) consent was recorded digitally. Underaged participants (<18 years) were urged to obtain assent from their parents/legal guardians, before filling in the survey. The survey took around 15 to 20 minutes for which they were not compensated. As a part of the demographics participants provided information regarding age, sex, gender identity, occupational status, COVID-19 related occupational setting, time zone/country of residence and native language as single-item demographic variables. The demographic characteristics of our sample are given in Table \@ref(tab:demotab).To ensure high data quality, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention. What is 4+5?"). Participants needed to confirm that they were participating the survey for the first time. 
Questions incorporating retrospective recall were all aligned to the period of "past four weeks". The data analysed in this study was collected between 17 May 2021 and 3 September 2021. 
```{r demotab, warning=F, message=F}
desc_kable  %>% kable_styling(latex_options = c("scale_down")) %>% landscape()
```

@@

Figure \@ref(fig:FlowchartFig) summarizes the steps of our psychometric analysis. In our analysis we used R (version 4.1.0), with several R packages. In the item generation and selection phase we had developed a item pool of 48 items with six-pont Likert type response format (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5:Always). Our purpose was to capture light exposure related behaviour and the first two response options: "Does not apply/I don't know" and "Never" were providing similar information. As such we decided to collapse them into one, making it a 5 point Likert type response format. We conducted an initial item analysis and proceed to the EFA with all 48 items. Prior to the EFA, necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed. Our data violated both the univariate and multivariate normality assumptions. Due to these violations and the ordinal nature of our response data, we used  polychoric correlation matrix [@desjardinsHandbookEducationalMeasurement2018] for the EFA. We employed principal axis (PA) as  factor extraction method with varimax rotation. PA is robust to the normality assumption violations [@watkinsStepbyStepGuideExploratory2020]. The obtained latent structure was confirmed by another factor extraction method: "the minimum residuals extraction" as well. We used a combination of factor identification method including scree plot [@cattellScreeTestNumber1966], minimum average partials method [@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers. Additionally, to determine the simple structure, we followed the common guidelines : (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading > .3 across factors [@bandalosFactorAnalysisExploratory2018]. We also conducted a EFA on non-merged response options data (Supp. Table \@ref(tab:efaunmerged)) and rejected the latent structure obtained as the factors were less interpretable.

For estimating reliability we used internal consistency reliability coefficient ordianl alpha. Though  Cronbach's alpha coefficient is widely used for estimating internal consistency, it has a tendency to deflate the estimates for  Likert type data since calculation is based on pearson-correlation matrix which requires response data to be continuous of nature [@gadermann2012estimating; @zumbo2007ordinal]. Subsequently to get  better estimates of reliability  we reported ordinal alpha for each factors that used polychoric-correlation matrix and assumed that the responses data were ordered in nature instead of continuous [@zumbo2007ordinal]. We also estimated the internal consistency reliability of the total scale using McDonald's $\omega_t$  coefficient which is a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use]. Both ordinal alpha and McDonald's $\omega_t$   coefficient value range from 0 to 1 and higher value represents better reliability.

@@

@@

## Initial development of items

## Large-scale  survey of instruments

### Participants

Table \@ref(tab:demotab) summarizes the survey participants' demographic characteristics. Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses. (XX??) participants were excluded from analysis due to not passing at least one of the "attention check" items. For exploring initial factor structure (EFA), a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013]. For estimating the sample size for the confirmatory factor analysis (CFA) we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where ten participants per parameter is required to earn trustworthiness of the result. Our sample size exceeds these requirements: Anonymous responses from a total of *n* = `r nrow(desctable.data)` participants were included in the analysis of the current study, split into samples for exploratory (EFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "1. EFA Sample",])`) and confirmatory factor analysis (CFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "2. CFA Sample",])`). The EFA sample included participants filling out the questionnaire from 17 May 2021 to XX XXX 2021, whereas participants who filled out the questionnaire from YY YYY 2021 to 3 September 2021 were included in the CFA analysis. Participants indicated filling out the online survey from a diverse range of geographic locations. The ten most common country and time zone combinations included:

@@

### Item Analysis

@@

### Exploratory Factor Analysis

```{r CorrMatrix, include=FALSE}
#This chunk holds code for producing correlation matrix and its details.

@@

Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy [@kaiserIndexFactorialSimplicity1974] . The overall KMO vale for 48 items was `r printnum(KMO$MSA)` which was above the cutoff value (.50) indicating a mediocre sample [@hutchesonMultivariateSocialScientist1999].  Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p < .001 indicated the correlations between items are adequate for the EFA. However only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than .30. The absolute value of inter-item correlation ranged between `r min.cor` to `r max.cor`. Figure \@ref(fig:figCor) depicts the correlation matrix.

```{r tabDes,results='asis'}
descriptives2 %>% 
apa_table(landscape =T,caption ="Descriptive Statistics", escape =F, font_size = "footnotesize", note = "*p<.001", align = c("p{1cm}","p{10cm}", rep("p{1cm}", ncol(descriptives2)))) 
```

@@

Scree plot ( Figure \@ref(fig:facIdFig)) suggested a six-factor solution. However, the minimum average partial (MAP) [@velicerDeterminingNumberComponents1976] method (Table \@ref(tab:factormp)) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:facIdFig)) suggested a five-factor solution. As a result, we tested both five-factor and six-factor solutions.

```{r factors, include=F}
#This chunk holds code for compiled factor identification plots

@@

### Confirmatory Factor Analysis

@@

Table \@ref(tab:tabCfa) summarizes the CFA fit indices of our fitted model. Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`); RMSEA = `r apa(fit.1[7],2,F)`,[`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 [`r Hmisc::label(sem.data$item32)`;`r Hmisc::label(sem.data$item33)`] and 16-17 [`r Hmisc::label(sem.data$item16)`;`r Hmisc::label(sem.data$item17)`]. Items pair 32-33 stemed from the preference of dimming electric device's brightness before bed time and items pair 16 and 19 stemed from the preference of using blue filtering or colored glasses during the daytime. Nevertheless, SRMR value was higher than the guideline (SRMR = `r apa(fit.1[10],2,F)`). Further by allowing one pair of items (30-41) [`r Hmisc::label(sem.data$item30)`;`r Hmisc::label(sem.data$item41)`] to covary their error variance and discarding two item (item 37 & 26) for very low r-square value, our model attained best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]) and SRMR value (SRMR = `r apa(fit.2[10],2,F)`) was also close to the suggestions of @huCutoffCriteriaFit1999. Internal consistency ordinal $\alpha$ for the five factors of LEBA were `r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)` respectively. Internal consistency McDonald's $\omega_t$ coefficient for the total scale was `r apa(rel.k[5,6],2,F)`. Figure \@ref(fig:figcfa) depicts the obtained CFA structure.

@@

### Measurement Invariance

```{r InvarianceAnalysis_data, include=FALSE}
#This chunk holds codes to prepare measurement invariance data.

@@

In our CFA sample we had `r mi.count[1,2]`  **native English speakers** and `r mi.count[2,2]` **non-native English speakers**  (For a detailed description these two groups see Sup. Table \@ref(tab:midesp) ). Table \@ref(tab:InvarianceTab) indicates our fitted model had acceptable fit indices for all of the fitted MI models. The model fit did not significantly decrease across the nested models indicating the acceptability of the highest measurement invariance model : residual model.

@@

### Semantic Analysis

"Semantic Scale Network"(SSN) analysis [@rosenbusch2020semantic] indicated that LEBA (23 items)  appeared most strongly related to scales about sleep: "Sleep Disturbance Scale For Children" [@bruni1996sleep] and "WHO-Composite International Diagnostic Interview (CIDI): Insomnia"[@who1990].The cosine similarities lie between .47 to .51. Flesch-Kincaid Grade Level [@flesch1948new] analysis on the the 23 items of our scale indicated required educational grade level was 3.33 and with a age above 8.33.

```{r textanalysis, include=F}
#This chunk holds codes for semantic analysis and readability test

@@

### Developing Short form of LEBA

We fitted each factor of LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =690). Item discrimination parameters of our tool fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level ($\theta$). Examination of the item information curve (Sup.fig \@ref(fig:IF)) indicated 5 items (1, 25,  38, 30, & 41) had relatively flat information curves (I($\theta$) <.20) thus discarded creating a short form of LEBA with 5 factors and 18 items.

@@
